--- 
title: "Regression Analysis using R and SAS"
author: "Sungchan Kang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This place is for writing regression book."
---

# Prerequisites

Before we talk about regression theory, we need to review some basic statistical inference methods and matrix algebra.

This book referred from many books including rowlings' "Applied Regression Analysis: A research Tool". 

A _matrix_ is a square-shaped array of numbers (sometimes can be string). In this book, boldface captial letters mean matrices. For example, 
$$
\mathbf{A}=
\begin{pmatrix}
65 & 154 \\
73 & 182 \\
68 &167
\end{pmatrix}.
$$
The numbers that form a matrix are called the elements of the matrix. A general matrix could be denoted as 
$$
\mathbf{A}=
\begin{bmatrix}
a_{11} & a_{12} & \cdots & a_{1n} \\
a_{21} & a_{22} & \cdots & a_{2n} \\
\vdots & \vdots & \cdots & \vdots \\
a_{m1} & a_{m2} & \cdots & a_{mn} 
\end{bmatrix}.
$$
$$


This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
